### 2025-05-08 course/csic5011/2025/project/project.tex
Add files via upload

\lecture{Final Project}{Yuan Yao}{Due: 23:59 30 April, 2024}{27 Mar, 2024}

@@

>>>>

\lecture{Final Project}{Yuan Yao}{Due: 23:59 April 29, 2025}{16 April, 2025}

@@

\newpage

\section{Final Submission}

\begin{enumerate}
\item HUANG Xinrui, ZENG Yeqin, GU Yanwu. Human Prefrontal Cortex Development Data. 4/27/2025. \\\
\item Zhang Tianyu, Cui Hanzhe, Qiu Wenxi, and Fu Erjia. Visualization of Rare Event and Importance Sampling Proposal in High-Dimensional Space. 4/29/2025. \\ 
\item Changlin He,  Lingjie Wei, and Jingwei Zhang, Unsupervised Learning on SNP Data: Subgroup Structure and Dimensionality Reduction. 4/28/2025. \\
\item Li William Thomas, Chen Zuorui. The topological structure of NeurIPS research articles. 4/28/2025. \\
\item Kunhan Lu, Lunlong Li and Shuhao Li, Evaluation of Manifold Learning Methods for Fashion-MNIST Embedding. 4/29/2025. \\
\item JIANG Peiqi, CHEN Yuheng and WU Jiacheng*. DIMENSION REDUCTION ANALYSIS BASED ON MNIST DATASET.  \\
\item Yequan BIE, Sunan HE, Yihui WANG and Weiwen ZHANG. Manifold Learning for NIPS Papers dataset. \\
\item XIE Zijun. Manifold Learning in Faces ordering. \\
\item Ding Ding, Zihao Zhang, Bingsong Gao. Comparative Analysis of Manifold Learning Methods for Face Pose Ordering. \\
\item Chuchu QIU, Haoyu WANG, Ran LIU, Yimeng QIAO. Single-Cell Analysis of Human Developmental Prefrontal Cortex Data. \\ 
\item Theodore Zbigniew Tyson. Generalised Learning Models for Human Age Ranking Based on Crowdsourced Comparisons.  \\
\item Kin Chit Alexander O. Canonical Correlation Analysis on Iris Flowers. \\
\item Ricky Tsz Wai CHAN, YANG Haowei. Unfolding the Market Geometry: A Topological and Manifold Learning Study of S\&P 500 Stocks. \\
\item Hyeonjae KIM. Evaluating Manifold Learning Techniques for Free Spoken Digit Dataset. \\
\item Biying HU, Bowei Zhang, Xiaoheng MA, Yuyao LIU. Prefrontal Cortex Development. \\
\item Ruihe WANG. HodgeRank-based Analysis of Crowdsourced Data. \\
\item CHU Yin King, LIU Ziyun, Hung Ka Yiu and Gamage Nanayakkara Dinusara Sasindu. PCA-Based Compression for Cardiac MRI Images. \\
\item Chung Chun Kit. Recovering 3D Protein Structures from Noisy Pairwise Distances. \\
\item Shen Xuanyu. PageRank and Chinese Universities. \\
\item FU Kai. Decomposing Zebrafish Swim Behaviors with Unsupervised Learning. \\
\item ZHAO, Puxuan. Comparative Dimensionality Reduction for S\&P 500: Stock Clustering and Visualization. \\
\end{enumerate}
